---
title: "R Notebook"
output: html_notebook
---

# Organizando el ambiente de trabajo 

```{r}
library(tidyverse)
library(tidygraph)
library(tidytext)
library(igraph)
library(sjrdata)
library(journalabbr)
library(openxlsx)
library(lubridate)
source("verbs.R")
library(bibliometrix)
```

# Preprocesamiento

## Cargando los datos

Cargamos los datos que Camilo seleccionó. En total son 176 datos. 

```{r}
data_consilidada_174 <- 
  read_csv("https://docs.google.com/spreadsheets/d/1iwBM_RY391OVuuK1XrXJdtDoVLim1BBJ/export?format=csv&gid=1070729370") |> filter(!duplicated(name))
           
```
Find data from Scopus 

```{r}
scopus_man_found_1 <- 
  tosr::tosr_load("data/scopus_1_10.bib", 
                  "data/scopus_11_20.bib",
                  "data/scopus_31_40.bib",
                  "data/scopus_41_50.bib",
                  "data/scopus_51_60.bib",
                  "data/scopus_61_70.bib",
                  "data/scopus_71_80.bib",
                  "data/scopus_81_90.bib",
                  "data/scopus_91_100.bib",
                  "data/scopus_111_120.bib",
                  "data/scopus_121_123.bib", 
                  "data/missing_97_74.bib",  # Second search
                  "data/coastal_management.bib", # Initial data
                  "data/coastal_management_1_500.txt", # Initial data
                  "data/coastal_management_501_1000.txt", # Initial data
                  "data/coastal_management_1001_1500.txt", # Initial data
                  "data/coastal_management_1501_2000.txt", # Initial data
                  "data/coastal_management_2001_2240.txt") # Initial data

scopus_man_found <- 
  scopus_man_found_1$df |> 
  filter(!duplicated(ID_TOS))
```

Merging both datasets 

```{r}
data_consilidada_174_123_found <- 
  data_consilidada_174 |> 
  left_join(scopus_man_found_1$df, by = c("name" = "ID_TOS")) |> 
  filter(!duplicated(name))
```

Organizing data for analysis

```{r}
reference_df <- 
  get_references(data_consilidada_174_123_found)

# country_df <- 
#   get_country()

journal_df <- 
  get_journals(data_consilidada_174_123_found, reference_df)

author_df <- 
  get_authors(data_consilidada_174_123_found, reference_df)
```


```{r}
wos_anual_production <- 
  data_consilidada_174_123_found |>
  filter(ref_type == "wos") |> 
  select(PY) |> 
  dplyr::count(PY, sort = TRUE) |> 
  na.omit()  |> 
  # filter(PY >= 2000,
  #        PY < year(today())) |> 
  mutate(ref_type = "wos")

scopus_anual_production  <- 
  data_consilidada_174_123_found |>
  filter(ref_type == "scopus") |>
  dplyr::count(PY, sort = TRUE) |> 
  na.omit() |> 
  # filter(PY >= 2000,
  #        PY < year(today())) |>
  mutate(ref_type = "scopus")

total_anual_production <- 
  data_consilidada_174_123_found |> 
  select(PY) |> 
  dplyr::count(PY, sort = TRUE) |> 
  na.omit() |> 
  # filter(PY >= 2000,
  #        PY < year(today())) |>
  mutate(ref_type = "total") |> 
  arrange(desc(PY))

range_years <- 
  range(min(wos_anual_production$PY), max(scopus_anual_production$PY))

range_years_tbl <- 
  tibble(PY = range_years[1]:range_years[2]) |> 
  mutate(PY = as.numeric(PY))

wos_anual_production_total <- 
  wos_anual_production |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(n = 0))|> 
  mutate(ref_type = "wos")

scopus_anual_production_total <- 
  scopus_anual_production |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(n = 0))|> 
  mutate(ref_type = "scopus")

total_anual_production_total <- 
  total_anual_production |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(n = 0))|> 
  mutate(ref_type = "total")
  
wos_scopus_total_annual_production <- 
  wos_anual_production_total |> 
  bind_rows(scopus_anual_production_total,
            total_anual_production_total) 

figure_1_data <-
  wos_scopus_total_annual_production |>
  mutate(PY = replace_na(PY, replace = 0)) |>
  pivot_wider(names_from = ref_type,
              values_from = n) |>
  arrange(desc(PY))
```

Time Cited from web of science

```{r}
TC_wos <- 
  data_consilidada_174_123_found |>
  filter(ref_type == "wos") |> 
  dplyr::select(PY, TC) |> 
  dplyr::group_by(PY) |> 
  dplyr::summarise(TC_sum = sum(TC)) |> 
  arrange(desc(PY)) |> 
  na.omit() |> 
  ungroup() |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(TC_sum = 0))
```

Time Cited from WoS

```{r}
TC_scopus <- 
  data_consilidada_174_123_found |>
  filter(ref_type == "scopus") |> 
  dplyr::select(PY, TC) |> 
  dplyr::group_by(PY) |> 
  dplyr::summarise(TC_sum = sum(TC)) |> 
  arrange(desc(PY)) |> 
  na.omit() |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(TC_sum = 0)) 
```

Time cited all

```{r}
TC_all <- 
  TC_scopus |> 
  left_join(TC_wos, 
            by = "PY", 
            suffix = c("_wos", 
                       "_scopus")) |> 
  replace_na(replace = list(TC_sum_scopus = 0)) |> 
  mutate(TC_sum_all = TC_sum_wos + TC_sum_scopus,
         TC_total = sum(TC_sum_all),
         TC_percentage = round(TC_sum_all/TC_total, digits = 2)) |> 
  select(PY, TC_sum_all, TC_percentage) |> 
  # filter(PY != 2022) |>
  # filter(PY >= 2000) |> 
  arrange(desc(PY)) |> 
  right_join(range_years_tbl) |> 
  replace_na(replace = list(TC_sum = 0))
```


# Analysis data

## Annual Scientific production 

```{r}

```



# Other 

## Organizando los datos

A estos datos les hace falta toda la información que se extrae de WoS y Scopus. 
Tenemos algunos datos en las consultas iniciales de WoS o Scopus. Por lo que, 
pegamos estos datos al data set de Camilo (data_consiliada). 

```{r}
data_consilidada_174_55_found <- 
  data_consilidada_174 |> 
  left_join(wos_scopus_tos$df, by = c("name" = "ID_TOS")) |> 
  filter(!duplicated(name))
```

En este dataset si está el AU_CO que necesitamos para hacer los análisis descriptivos. 

Seleccionando los datos que faltan

```{r}
data_consilidada_174_119_missing <- 
  data_consilidada_174_55_found |> 
  filter(is.na(AU)) |> 
  select(name, full_name)
```

Leyendo los datos de Scopus que se encontraron a partir de los títulos

```{r}
# scopus_man_found_1 <- 
#   tosr::tosr_load("data/scopus_1_10.bib", 
#                   "data/scopus_11_20.bib",
#                   "data/scopus_31_40.bib",
#                   "data/scopus_41_50.bib",
#                   "data/scopus_51_60.bib",
#                   "data/scopus_61_70.bib",
#                   "data/scopus_71_80.bib",
#                   "data/scopus_81_90.bib",
#                   "data/scopus_91_100.bib",
#                   "data/scopus_111_120.bib",
#                   "data/scopus_121_123.bib",
#                   "data/missing_97_74.bib",
#                   "data/coastal_management.bib", # Initial data
#                   "data/coastal_management_1_500.txt", # Initial data
#                   "data/coastal_management_501_1000.txt", # Initial data
#                   "data/coastal_management_1001_1500.txt", # Initial data
#                   "data/coastal_management_1501_2000.txt", # Initial data
#                   "data/coastal_management_2001_2240.txt") # Initial data

# scopus_man_found_1_87 <- 
#   scopus_man_found_1$df
# 
# scopus_man_found_2_28 <- 
#   read_csv("https://docs.google.com/spreadsheets/d/1iwBM_RY391OVuuK1XrXJdtDoVLim1BBJ/export?format=csv&gid=1360214247")|> 
#   mutate(PN = as.character(PN),
#          VL = as.character(VL))
# 
# scopus_man_found <- 
#   scopus_man_found_1_87 |> 
#   bind_rows(scopus_man_found_2_28) 


# data_consolidada_174_119_63_found <- 
#   data_consilidada_174_119_missing |> 
#   left_join(scopus_man_found_1_87, by = c("name" = "ID_TOS")) |> 
#   filter(!is.na(AU))
# 
# data_consolidada_174_119_56_missing <- 
#   data_consilidada_174_119_missing |> 
#   left_join(scopus_man_found_1_87, by = c("name" = "ID_TOS")) |> 
#   filter(is.na(AU))

# data_consolidada_176_126_67_missing |> 
#   mutate(year = str_extract(name, "[0-9]{4}")) |> 
#   select(name, full_name, year) |> 
#   write_csv("data/data_consolidada_176_126_67_missing.csv")

# scopus_man_found_2_28 <- 
#   tosr::tosr_load("data/missing_67_found_28.bib")

# scopus_man_found_2_28 <- 
#   read_csv("https://docs.google.com/spreadsheets/d/1iwBM_RY391OVuuK1XrXJdtDoVLim1BBJ/export?format=csv&gid=1360214247")
# 
# data_consolidada_176_56_40_missing <- 
#   data_consolidada_174_119_56_missing |> 
#   select(name, full_name) |>  
#   left_join(scopus_man_found_2_28, by = c("name" = "ID_TOS")) |> 
#   filter(is.na(AU))

# scopus_man_found <- 
#   read_csv("data/scopus_encontrados.csv")

# data_consilidada_full_36 <- 
#   data_consilidada_2 |> 
#   left_join(scopus_man_found, 
#             by = c("name" = "ID_TOS")) |> 
#   filter(!is.na(AU))
# 
# data_consilidada_missing_97 <- 
#   data_consilidada_2 |> 
#   left_join(scopus_man_found, 
#             by = c("name" = "ID_TOS")) |> 
#   filter(is.na(AU))

```

Merging the 119 missing values with Scopus found dataset. 

```{r}
data_consolidada_174_123_found <- 
  data_consilidada_174 |> 
  left_join(scopus_man_found, by = c("name" = "ID_TOS")) |> 
  filter(!is.na(AU))
```


```{r}
# data_consilidada_174_55_found <- 
#   data_consilidada_174 |> 
#   left_join(scopus_man_found_1_87, 
#             by = c("name" = "ID_TOS")) |> 
#   filter(!duplicated(name))

```


Merging whole data with found data in scopus 

```{r}
data_consilidada_174_55_found |> select(-subfield, -year, -"...5", "ref_type") |> names()
select("name",      "full_name", "AU",        "ID",         "C1",        "CR",       "JI",         "AB",      "RP",
       "PA",        "AR",        "RP",        "DT",        "DI",        "FU",        "SN",        "SO",        "LA",
       "TC",        "PN" ,       "PU",        "PM",        "DB",        "TI",        "VL",        "PY",        "FX",
       "AU_UN",     "AU1_UN",    "AU_UN_NR",  "SR_FULL",   "SR",        "AU_CO")
```


```{r}
data_consolidada_174_119_84_found |> names() 
select("name",      "full_name", "AU",        "ID",        "C1"  ,      "CR"   ,     "JI"   ,     "AB"     ,   "RP"      , 
       "DT"    ,    "DI"  ,      "SN"   ,     "SO"    ,    "LA"    ,    "TC"  ,      "PN"  ,      "PP" ,       "PU"  ,     
       "DB"    ,    "TI"   ,     "url"  ,     "VL"     ,   "PY"   ,     "AU_UN"   ,  "AU1_UN" ,   "AU_UN_NR" , "SR_FULL"  ,
       "SR"    ,    "AU_CO"   ,  "ref_type" , "DE"  ,      "PA" ,       "AR"   ,     "coden" ,    "FU"    ,    "BN"  ,     
       "PM"    ,    "sponsors" , "FX" ,       "SR_TOS")
```

Tidying data 

```{r}
data_consilidada_174_55_found |> select(-subfield, -year, -"...5")
```



Merging scopus with scopus found

```{r}

data_consilidada_full_43 <- 
  data_consilidada_1 |> 
  filter(!is.na(AU)) 


data_consiliada_full_79 <- 
  data_consilidada_full_43 |>  
  select(-subfield, -year, -AU_CO) |> 
  bind_rows(data_consilidada_full_36 |> 
              select(-coden, -BN, -page_count, -sponsors, 
                     -PP, -url, -SR_TOS) |> 
              mutate(PN = as.character(PN),
                     PM = as.character(PM))) 

data_consolidada_97_missing <- 
  data_consilidada_1 |> 
  left_join()
  data_consiliada_full_79 |> 
  
```

Finding missing values 79

```{r}
data_consolidada_97_missing_format <- 
  data_consilidada_missing_97 |> 
  mutate(year = str_extract(name, "[0-9]{4}"))

data_consolidada_97_missing_format |> 
  select(name, full_name, year) |> 
  write_csv("data/data_consolidada_97_missing.csv")

data_consolidada_176_126_68_missing |> 
  mutate(year = str_extract(name, "[0-9]{4}")) |> 
  select(name, full_name, year) |> 
  write_csv("data/data_consolidada_176_126_68_missing.csv")

```

We found through manually search in Scopus

```{r}
scopus_missing_97_74 <- 
  tosr::tosr_load("data/missing_97_74.bib")

data_consolidada_97_74 <- 
  data_consilidada_missing_97 |> 
  select(name, full_name) |> 
  left_join(scopus_missing_97_74$df, by = c("name" = "ID_TOS")) |> 
  filter(!duplicated(name))

data_missing_97_66 <- 
  data_consolidada_97_74 |> 
  filter(is.na(AU))

data_full_97_ <- 
  data_consolidada_97_74 |> 
  filter(!is.na(AU))

```

Merging full data 

```{r}

```



```{r}
wos_anual_production <- 
  data_consiliada_full_79 |> 
  filter(ref_type == "wos") |> 
  select(PY) |>
  dplyr::count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(#PY >= 2000,
         PY < year(today())) |> 
  mutate(ref_type = "wos") 

scopus_anual_production  <- 
  data_consiliada_full_79 |> 
  filter(ref_type == "scopus")  |> 
  select(PY) |> 
  dplyr::count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(#PY >= 2000,
         PY < year(today())) |>
  mutate(ref_type = "scopus") 

total_anual_production <- 
  data_consiliada_full_79 |> 
  select(PY) |> 
  dplyr::count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(#PY >= 2000,
         PY < year(today())) |>
  mutate(ref_type = "total") |> 
  arrange(desc(PY))

wos_scopus_total_annual_production <- 
  wos_anual_production |> 
  bind_rows(scopus_anual_production,
            total_anual_production) 

# Checking results of total
wos_scopus_total_annual_production_dummy <- 
  total_anual_production |> 
  dplyr::rename(n_total = n,
                ref_type_total = ref_type) |> 
  left_join(wos_anual_production |> 
              dplyr::rename(n_wos = n,
                            ref_type_wos = ref_type) ) |> 
  left_join(scopus_anual_production |> 
              dplyr::rename(n_scopus = n,
                            ref_type_scopus = ref_type)) |> 
  mutate(total = if_else(n_total < n_wos | n_total < n_scopus, 
                         n_scopus, # it could be improved
                         n_total)) |> 
  replace_na(list(n_wos = 0, 
                  n_scopus = 0, 
                  total = 0,
                  ref_type_wos = "wos",
                  ref_type_scopus = "scopus"))

wos_scopus_total_annual_production_total <- 
  wos_scopus_total_annual_production_dummy |> 
  select(PY, 
         n = total,
         ref_type = ref_type_total)

wos_scopus_total_annual_production_scopus <- 
  wos_scopus_total_annual_production_dummy |> 
  select(PY, 
         n = n_scopus,
         ref_type = ref_type_scopus)

wos_scopus_total_annual_production_wos <- 
  wos_scopus_total_annual_production_dummy |> 
  select(PY, 
         n = n_wos,
         ref_type = ref_type_wos)

wos_scopus_total_annual_production <- 
  wos_scopus_total_annual_production_total |> 
  bind_rows(wos_scopus_total_annual_production_scopus,
            wos_scopus_total_annual_production_wos) 

figure_1_data <-
  wos_scopus_total_annual_production |>
  mutate(PY = replace_na(PY, replace = 0)) |>
  pivot_wider(names_from = ref_type,
              values_from = n) |>
  arrange(desc(PY)) |> 
  mutate(total = scopus + wos) 

# Creating the range of missing years

range_tbl <- 
  tibble(PY = range(figure_1_data$PY)[1]:range(figure_1_data$PY)[2]) |> 
  mutate(PY = as.numeric(PY))

figure_1_data_all_years <- 
  figure_1_data |> 
  right_join(range_tbl) |> 
  mutate(across(everything(), ~replace_na(.x, 0)))
```

I would like to create a bar graph of WoS and Scopus data

We need to identify the times cited variable for each database and later sum them all.

Time Cited from web of science

```{r}
TC_wos <- 
  data_consiliada_full_79 |> 
  filter(ref_type == "wos") |> 
  dplyr::select(PY, TC) |> 
  dplyr::group_by(PY) |> 
  dplyr::summarise(TC_sum = sum(TC)) |> 
  arrange(desc(PY)) |> 
  na.omit() 
```

Time Cited from WoS

```{r}
TC_scopus <- 
  data_consiliada_full_79 |> 
  filter(ref_type == "scopus") |> 
  dplyr::select(PY, TC) |> 
  dplyr::group_by(PY) |> 
  dplyr::summarise(TC_sum = sum(TC)) |> 
  arrange(desc(PY)) |> 
  na.omit() 
```

Time cited all

```{r}
TC_all <- 
  TC_scopus |> 
  left_join(TC_wos, 
            by = "PY", 
            suffix = c("_wos", 
                       "_scopus")) |> 
  replace_na(replace = list(TC_sum_scopus = 0)) |> 
  mutate(TC_sum_all = TC_sum_wos + TC_sum_scopus,
         TC_total = sum(TC_sum_all),
         TC_percentage = round(TC_sum_all/TC_total, digits = 2)) |> 
  select(PY, TC_sum_all, TC_percentage) |> 
  # filter(PY != 2022) |>
  # filter(PY >= 2000) |> 
  arrange(desc(PY))
```

# Descriptive Analysis

## Scientific Production

## Figure 1a - Scopus + WoS

Probando una nueva opción

```{r}
figure_1_all <- 
data_consilidada_1 |> 
  select(ID_TOS = name, year, ref_type) |> 
  left_join(scopus_man_found |> 
              select(ID_TOS) |> 
              mutate(scopus = "scopus"), by = "ID_TOS") |> 
  mutate(ref_type = if_else(is.na(ref_type) , 
                            scopus, ref_type )) |> 
  select(-scopus) |> 
  mutate(ref_type = if_else(is.na(ref_type), "other", ref_type))

```


```{r}



figure_1a <- 
  figure_1_data_all_years |> 
  pivot_longer(!PY, names_to = "ref_type", values_to = "n") |> 
  filter(ref_type != "total") |> 
  ggplot(aes(x = factor(PY), 
             y = n, 
             fill = ref_type)) +
  geom_bar(stat = "identity", 
           position = "dodge") +
  geom_text(aes(label = n),
            vjust = -0.3,
            position = position_dodge(0.9),
            size = 3,
            family = "Times") +
  scale_fill_manual(values = c("springgreen3",
                               "orange3")) +
  theme(text = element_text(family = "Times",
                            face = "bold",
                            size =12),
        panel.background = element_rect(fill = "white"),
        legend.position = "bottom",
        legend.title = element_text(size = 0),
        axis.text.x = element_text(face = "bold", 
                                   angle = 45, 
                                   vjust = 0.5),
        axis.line = element_line(color = "black", 
                                 size = 0.2)) +
  labs(y = "Number of publications", 
       x = "Year") 

figure_1a
```

```{r}
data_consilidada |> 
  select(year) |> 
  group_by(year) |> 
  count() |> 
  ggplot(aes(x = factor(year),
             y = n, 
             group = 1)) +
  geom_line(stat = "identity") +
  geom_point() 
```

## Country analysis

## Table 2 - Country production

```{r}
wos_scopus_countries <- 
  data_consiliada_full_79 |> 
  select(SR, AU_CO, TC) |> 
  separate_rows(AU_CO, sep = ";") |> 
  unique() |> 
  drop_na()

wos_scopus_countries_journals <- 
  wos_scopus_countries |> 
  left_join(wos_scopus_tos$df |> 
              select(SR, SO, PY), 
            by = "SR")

scimago_2020 <- 
  read_csv2("data/scimago2020.csv") |> 
  select(SO = Title,
         quartile = "SJR Best Quartile") |> 
  mutate(PY = 2020)

scimago_2021 <- 
  read_csv2("data/scimago2020.csv") |> 
  select(SO = Title,
         quartile = "SJR Best Quartile") |> 
  mutate(PY = 2021)

scimago_2020_2021 <- 
  scimago_2020 |> 
  bind_rows(scimago_2021) |> 
  select(PY, SO, quartile)

scimago <- 
  sjr_journals |> 
  select(PY = year, 
         SO = title,
         quartile = sjr_best_quartile) |> 
  mutate(SO = str_to_upper(SO),
         PY = as.numeric(PY)) |> 
  bind_rows(scimago_2020_2021)

wos_scopus_countries_journals_scimago <- 
  wos_scopus_countries_journals |> 
  left_join(scimago, by = c("PY", "SO")) |>  
  drop_na() |> 
  select(AU_CO, TC, quartile) |> 
  filter(quartile != "-")
```

### Table 2a - production

Production per country

```{r}
table_2a <- 
  wos_scopus_countries |> 
  select(AU_CO) |> 
  group_by(AU_CO) |> 
  summarise(count_co = n()) |> 
  mutate(percentage_co = count_co / sum(count_co) * 100,
         percentage_co = round(percentage_co, digits = 2)) |> 
  arrange(desc(count_co))
table_2a 
```

Total percentage of the top 10 Countries

```{r}
table_2a |> 
  slice(1:10) |> 
  select(percentage_co) |> 
  summarise(total_sum_per = sum(percentage_co)) |> 
  pull()
```

### Table 2b - citations

Citations received per country

```{r}
table_2b <- 
  wos_scopus_countries_journals_scimago |> 
  select(AU_CO, TC) |> 
  group_by(AU_CO) |> 
  summarise(citation = sum(TC)) |> 
  mutate(percentage_ci = citation / sum(citation) * 100) |> 
  arrange(desc(citation))
table_2b
```

Total percentage of citation of the top 10 countries

```{r}
table_2b |> 
  slice(1:10) |> 
  select(percentage_ci) |> 
  summarise(total_sum_per = sum(percentage_ci)) |> 
  pull()
```

### Table 2c - Quartiles

```{r}
table_2c <- 
  wos_scopus_countries_journals_scimago |> 
  select(AU_CO, quartile) |> 
  group_by(AU_CO) |> 
  count(quartile, sort = TRUE) |> 
  pivot_wider(names_from = quartile, 
              values_from = n) |> 
  select(AU_CO, Q1, Q2, Q3, Q4) |> 
  mutate(Q1 = replace_na(Q1, 0),
         Q2 = replace_na(Q2, 0),
         Q3 = replace_na(Q3, 0),
         Q4 = replace_na(Q4, 0))
table_2c
```

### Table 2 - Final

Merging all tables 2

```{r}
table_2 <- 
  table_2a |> 
  left_join(table_2b, by = "AU_CO") |> 
  left_join(table_2c, by = "AU_CO") |> 
  slice(1:10)
table_2 |> 
  filter(!is.na(AU_CO))
```

## Figure 2 - Country Collaboration

Exporting data to biblioshiny

```{r}
write.xlsx(x = wos_scopus_tos$df, file = "output/wos_scopus.xlsx")
```
