---
title: "R Notebook"
output: 
  html_document:
            toc: TRUE
            toc_float: TRUE
---

# Creating the environment 

```{r}
library(tidyverse)
library(lubridate)
library(sjrdata)
library(igraph)
library(tidygraph)
library(ggraph)
library(bibliometrix)
```

# Getting data 

All data is here:

https://docs.google.com/spreadsheets/d/1nwszUhhHBzJS1WA0aP5lVMZY_lEVxjT4QO1l3bKiVtE/edit#gid=0

```{r}
mzc_data <- 
  read_csv("https://docs.google.com/spreadsheets/d/1iwBM_RY391OVuuK1XrXJdtDoVLim1BBJ/export?format=csv&gid=1611166548") |> 
  filter(!is.na(ref_type))

figure_1_data <- 
  read_csv("https://docs.google.com/spreadsheets/d/1nwszUhhHBzJS1WA0aP5lVMZY_lEVxjT4QO1l3bKiVtE/export?format=csv&gid=1442849006")

TC_all <- 
  read_csv("https://docs.google.com/spreadsheets/d/1nwszUhhHBzJS1WA0aP5lVMZY_lEVxjT4QO1l3bKiVtE/export?format=csv&gid=1467009091")

journal_df <- 
  read_csv("https://docs.google.com/spreadsheets/d/1nwszUhhHBzJS1WA0aP5lVMZY_lEVxjT4QO1l3bKiVtE/export?format=csv&gid=1871024023")

author_df <- 
  read_csv("https://docs.google.com/spreadsheets/d/1nwszUhhHBzJS1WA0aP5lVMZY_lEVxjT4QO1l3bKiVtE/export?format=csv&gid=640727835")
```

# Data Analysis

# 3.1 Scientific Production

```{r}
figure_1a <- 
  figure_1_data |> 
  pivot_longer(!PY, names_to = "ref_type", values_to = "n") |> 
  filter(ref_type != "total") |> 
  ggplot(aes(x = factor(PY), 
             y = n, 
             fill = ref_type)) +
  geom_bar(stat = "identity", 
           position = "dodge") +
  geom_text(aes(label = n),
            vjust = -0.3,
            position = position_dodge(0.9),
            size = 3,
            family = "Times") +
  scale_fill_manual(values = c("springgreen3",
                               "orange3")) +
  theme(text = element_text(family = "Times",
                            face = "bold",
                            size =12),
        panel.background = element_rect(fill = "white"),
        legend.position = "bottom",
        legend.title = element_text(size = 0),
        axis.text.x = element_text(face = "bold", 
                                   angle = 45, 
                                   vjust = 0.5),
        axis.line = element_line(color = "black", 
                                 size = 0.2)) +
  labs(y = "Number of publications", 
       x = "Year") 

figure_1a
```



## Figure 1c - Citations

```{r}
figure_1c <- 
  TC_all |> 
  ggplot(aes(x = PY , y = TC_sum_all)) +
  geom_line(stat = "identity", color = "purple") +
  geom_point(color = "purple") +
  scale_x_continuous(breaks = seq(1974, year(today()) , by = 1)) +
  geom_text(aes(label = TC_sum_all),
            vjust = -0.3,
            position = position_dodge(0.9),
            size = 3,
            family = "Times", 
            color = "purple") +
  scale_fill_manual(values = c("springgreen3",
                               "orange3")) +
  theme(text = element_text(family = "Times",
                            face = "bold",
                            size =12),
        panel.background = element_rect(fill = "white"),
        legend.position = "bottom",
        legend.title = element_text(size = 0),
        axis.text.x = element_text(face = "bold", 
                                   angle = 45, 
                                   vjust = 0.5),
        axis.line = element_line(color = "black", 
                                 size = 0.2)) +
  labs(y = "Number of citations", 
       x = "Year") 
figure_1c
```

# 3.2 Country analysis

## Table 2 - Country production

```{r}
wos_scopus_countries <- 
  mzc_data |> 
  select(SR, AU_CO, TC) |> 
  separate_rows(AU_CO, sep = ";") |> 
  unique() |> 
  drop_na()

wos_scopus_countries_journals <- 
  wos_scopus_countries |> 
  left_join(mzc_data |> 
              select(SR, SO, PY), 
            by = "SR")

scimago_2020 <- 
  read_csv2("scimago2020.csv", show_col_types = FALSE) |> 
  select(SO = Title,
         quartile = "SJR Best Quartile") |> 
  mutate(PY = 2020)

scimago_2021 <- 
  read_csv2("scimago2020.csv", show_col_types = FALSE) |> 
  select(SO = Title,
         quartile = "SJR Best Quartile") |> 
  mutate(PY = 2021)

scimago_2020_2021 <- 
  scimago_2020 |> 
  bind_rows(scimago_2021) |> 
  select(PY, SO, quartile)

scimago <- 
  sjrdata::sjr_journals |> 
  select(PY = year, 
         SO = title,
         quartile = sjr_best_quartile) |> 
  mutate(SO = str_to_upper(SO),
         PY = as.numeric(PY)) |> 
  bind_rows(scimago_2020_2021)

wos_scopus_countries_journals_scimago <- 
  wos_scopus_countries_journals |> 
  left_join(scimago, by = c("PY", "SO")) |>  
  drop_na() |> 
  select(AU_CO, TC, quartile) |> 
  filter(quartile != "-")
```

### Table 2a - production

Production per country

```{r}
table_2a <- 
  wos_scopus_countries |> 
  dplyr::select(AU_CO) |> 
  dplyr::group_by(AU_CO) |> 
  dplyr::summarise(count_co = n()) |> 
  dplyr::mutate(percentage_co = count_co / sum(count_co) * 100,
                percentage_co = round(percentage_co, digits = 2)) |> 
  dplyr::arrange(desc(count_co))
 
```

### Table 2b - citations

Citations received per country

```{r}
table_2b <- 
  wos_scopus_countries_journals_scimago |> 
  dplyr::select(AU_CO, TC) |> 
  dplyr::group_by(AU_CO) |> 
  dplyr::summarise(citation = sum(TC)) |> 
  dplyr::mutate(percentage_ci = citation / sum(citation) * 100) |> 
  dplyr::arrange(desc(citation))
```

### Table 2c - Quartiles

```{r}
table_2c <- 
  wos_scopus_countries_journals_scimago |> 
  dplyr::select(AU_CO, quartile) |> 
  dplyr::group_by(AU_CO) |> 
  dplyr::count(quartile, sort = TRUE) |> 
  pivot_wider(names_from = quartile, 
              values_from = n) |> 
  dplyr::select(AU_CO, Q1, Q2, Q3, Q4) |> 
  dplyr::mutate(Q1 = replace_na(Q1, 0),
                Q2 = replace_na(Q2, 0),
                Q3 = replace_na(Q3, 0),
                Q4 = replace_na(Q4, 0))
```

### Table 2 - Final

Merging all tables 2

```{r}
table_2 <- 
  table_2a |> 
  left_join(table_2b, by = "AU_CO") |> 
  left_join(table_2c, by = "AU_CO") |> 
  mutate(percentage_ci = round(percentage_ci, digits = 2)) |> 
  slice(1:10)
table_2 |>
  DT::datatable(class = "cell-border stripe", 
                rownames = F, 
                filter = "top", 
                editable = FALSE, 
                extensions = "Buttons", 
                options = list(dom = "Bfrtip",
                               buttons = c("copy",
                                           "csv",
                                           "excel", 
                                           "pdf", 
                                           "print")))
```

## Figure 2 - Country Collaboration

Exporting data to biblioshiny

```{r}
# write.xlsx(x = wos_scopus_tos$df, file = "wos_scopus.xlsx")
```

# 3.3 Journal Analysis

## Table 3 Most productive scientific journals

```{r}
table_1 <- 
  tibble(wos = length(mzc_data |> 
                        select(ref_type) |> 
                        filter(ref_type == "wos") |>
                        pull()), # Create a dataframe with the values.
         scopus = length(mzc_data |> 
                        select(ref_type) |> 
                        filter(ref_type == "scopus") |>
                        pull()), 
         total = length(mzc_data$ref_type))

wos_journal <- 
  mzc_data |> 
  dplyr::filter(ref_type == "wos") |> 
  dplyr::select(journal = SO) |> 
  na.omit() |> 
  dplyr::count(journal, sort = TRUE) |> 
  dplyr::slice(1:20) |> 
  dplyr::rename(publications = n) |> 
  dplyr::mutate(database = "wos")

scopus_journal <- 
  mzc_data |> 
  filter(ref_type == "scopus") |> 
  dplyr::select(journal = SO) |> 
  na.omit() |> 
  dplyr::count(journal, sort = TRUE) |> 
  dplyr::slice(1:20) |> 
  dplyr::rename(publications = n) |> 
  dplyr::mutate(database = "scopus")

total_journal <- 
  mzc_data |> 
  dplyr::select(journal = SO) |> 
  na.omit() |> 
  dplyr::count(journal, sort = TRUE) |> 
  dplyr::slice(1:20) |> 
  dplyr::rename(publications = n) |> 
  dplyr::mutate(database = "total")

wos_scopus_total_journal <- 
  wos_journal |> 
  dplyr::bind_rows(scopus_journal, 
                   total_journal) |> 
  pivot_wider(names_from = database, 
              values_from = publications) |> 
  dplyr::arrange(desc(total)) |> 
  dplyr::slice(1:10) |> 
  dplyr::mutate_all(~replace_na(., 0)) |> 
  dplyr::mutate(percentage = total / table_1 |> 
                  dplyr::pull(total),
                percentage = round(percentage, digits = 2))


wos_scopus_total_journal
```

## Scopus Journal Citation Network

Creating the graph object

```{r}

journal_citation_graph_weighted_tbl_small <- 
  journal_df |> 
  dplyr::select(JI_main, JI_ref) |> 
  dplyr::group_by(JI_main, JI_ref) |> 
  dplyr::count() |> 
  dplyr::rename(weight = n) |> 
  as_tbl_graph(directed = FALSE) |> 
  # convert(to_simple) |> 
  activate(nodes) |> 
  dplyr::mutate(components = tidygraph::group_components(type = "weak"))  |> 
  dplyr::filter(components == 1) |> 
  activate(nodes) |> 
  dplyr::mutate(degree = centrality_degree(),
                community = tidygraph::group_louvain()) |> 
  dplyr::select(-components) |> 
  dplyr::filter(degree >= 1)
# activate(edges) |>
# dplyr::filter(weight != 1)

communities <- 
  journal_citation_graph_weighted_tbl_small |> 
  activate(nodes) |> 
  data.frame() |> 
  dplyr::count(community, sort = TRUE) |> 
  dplyr::slice(1:10) |> 
  dplyr::select(community) |> 
  dplyr::pull()
# Filtering biggest communities 
journal_citation_graph_weighted_tbl_small_fig <- 
  journal_citation_graph_weighted_tbl_small |> 
  activate(nodes) |> 
  dplyr::filter(community %in% communities)

```

## Figure 3 Journal Citation Network

Selecting nodes to show

```{r}
jc_com_1 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[1]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_2 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[2]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_3 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[3]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_4 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[4]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_5 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[5]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_6 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[6]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_7<- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[7]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_8 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[8]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_9 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[9]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com_10 <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(community == communities[10]) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  dplyr::arrange(desc(degree)) |> 
  dplyr::slice(1:10) |> 
  data.frame() |> 
  dplyr::select(name)
jc_com <- 
  jc_com_1 |> 
  bind_rows(jc_com_2,
            jc_com_3,
            # jc_com_4,
            # jc_com_5,
            # jc_com_6,
            # jc_com_7,
            # jc_com_8,
            # jc_com_9,
            # jc_com_10
  )
```

### Figure 3a Journal Citation

```{r}
figure_3a <- 
  journal_citation_graph_weighted_tbl_small_fig |> 
  activate(nodes) |> 
  dplyr::filter(name %in% jc_com$name) |>
  dplyr::mutate(degree = centrality_degree(),
                community = factor(community)) |> 
  dplyr::filter(degree != 0) |> 
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(width = weight),
                 colour = "lightgray") +
  scale_edge_width(name = "Link strength") +
  geom_node_point(aes(color = community, 
                      size = degree)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_size(name = "Degree") +
  # scale_color_binned(name = "Communities") +
  theme_graph()
figure_3a
```

### Figure 3b clusters

```{r}
figure_3b <- 
  journal_citation_graph_weighted_tbl_small |> 
  activate(nodes) |> 
  data.frame() |> 
  dplyr::select(community) |> 
  dplyr::count(community, sort = TRUE) |> 
  dplyr::slice(1:10) |> 
  ggplot(aes(x = reorder(community, n), y = n)) +
  geom_point(stat = "identity") +
  geom_line(group = 1) + 
  # geom_text(label = as.numeric(community),
  #           nudge_x = 0.5,
  #           nudge_y = 0.5,
  #           check_overlap = T) +
  labs(title = "Communities by size", 
       x = "communities", 
       y = "Journals") +
  theme(text = element_text(color = "black",
                            face = "bold",
                            family = "Times New Roman"),
        plot.title = element_text(size = 25),
        panel.background = element_rect(fill = "white"), 
        axis.text.y = element_text(size = 15, 
                                   colour = "black"),
        axis.text.x = element_text(size = 15,
                                   colour = "black"),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) 
figure_3b
```

# 3.1.4 Author Analysis

Table 4

```{r}

data_biblio_wos <- biblioAnalysis(mzc_data |> 
                                    filter(ref_type == "wos") |> 
                                    data.frame())

wos_authors <- 
  data_biblio_wos$Authors |> 
  data.frame() |> 
  dplyr::rename(authors_wos = AU, papers_wos = Freq) |> 
  dplyr::arrange(desc(papers_wos)) |> 
  dplyr::slice(1:10) |> 
  dplyr::mutate(database_wos = "wos")

data_biblio_scopus <- biblioAnalysis(mzc_data |> 
                                    filter(ref_type == "scopus") |> 
                                    data.frame())

scopus_authors <- 
  data_biblio_scopus$Authors |> 
  data.frame() |> 
  dplyr::rename(authors_scopus = AU, papers_scopus = Freq) |> 
  dplyr::arrange(desc(papers_scopus)) |> 
  dplyr::slice(1:10) |> 
  dplyr::mutate(database_scopus = "scopus")

data_biblio_total <- biblioAnalysis(mzc_data)

total_authors <- 
  data_biblio_total$Authors |> 
  data.frame() |> 
  dplyr::rename(authors_total = AU, 
                papers_total = Freq) |> 
  dplyr::arrange(desc(papers_total)) |> 
  dplyr::slice(1:10) |> 
  dplyr::mutate(database_total = "total")

wos_scopus_authors <- 
  wos_authors |> 
  dplyr::bind_cols(scopus_authors,
                   total_authors) 

wos_scopus_authors
```

Creating the ASN - graph object

```{r}
author_network_time <- 
  author_df |> 
  tidygraph::as_tbl_graph(directed = FALSE) |> 
  activate(nodes) |> 
  # dplyr::mutate(components = tidygraph::group_components(type = "weak")) |> 
  # dplyr::filter(components == 1) |> 
  dplyr::mutate(degree = centrality_degree(),
                community = as.factor(group_louvain()))

author_network <- 
  author_df |> 
  dplyr::select(-PY) |> 
  dplyr::group_by(from, to) |> 
  dplyr::count() |> 
  dplyr::rename(weight = n) |> 
  tidygraph::as_tbl_graph(directed = FALSE) |> 
  activate(nodes) |> 
  # dplyr::mutate(components = tidygraph::group_components(type = "weak")) |> 
  # dplyr::filter(components == 1) |> 
  dplyr::mutate(degree = centrality_degree(),
                community = as.factor(group_louvain()))

```


### Figure 4a clusters of each community

```{r}
figure_4a <- 
  author_network |> 
  activate(nodes) |> 
  data.frame() |> 
  dplyr::count(community) |>
  slice(1:10) |>  
  ggplot(aes(x = reorder(community, n), y = n)) +
  geom_point(stat = "identity") +
  geom_line(group = 1) + 
  # geom_text(label = as.numeric(community),
  #           nudge_x = 0.5,
  #           nudge_y = 0.5,
  #           check_overlap = T) +
  labs(title = "Communities by size", 
       x = "communities", 
       y = "Authors") +
  theme(text = element_text(color = "black",
                            face = "bold",
                            family = "Times New Roman"),
        plot.title = element_text(size = 25),
        panel.background = element_rect(fill = "white"), 
        axis.text.y = element_text(size = 15, 
                                   colour = "black"),
        axis.text.x = element_text(size = 15,
                                   colour = "black"),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) 

figure_4a
```

### Figure 4b Longitudinal data of ASN

```{r}
# Create a dataframe with links 
fig_1c_edges <- 
  author_network_time |>
  activate(edges) |> 
  as_tibble() |> 
  dplyr::select(year = PY) |> 
  dplyr::count(year) |> 
  dplyr::filter(year >= 2000,
                year <= 2022) |> 
  dplyr::mutate(percentage = n/max(n)) |> 
  dplyr::select(year, percentage)
# Create a data frame with author and year 
fig_1c_nodes <- # 21 row 
  author_network_time |>
  activate(edges) |> 
  as_tibble() |> 
  dplyr::select(author = from, 
                year = PY) |>
  bind_rows(author_network_time |> 
              activate(edges) |> 
              as_tibble() |> 
              dplyr::select(author = to, 
                            year = PY)) |> 
  unique() |> 
  dplyr::group_by(author) |> 
  dplyr::slice(which.min(year)) |>
  dplyr::ungroup() |> 
  dplyr::select(year) |> 
  dplyr::group_by(year) |> 
  dplyr::count(year) |> 
  dplyr::filter(year >= 2000,
                year <= 2022) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(percentage = n / max(n)) |> 
  select(year, percentage)
```

plotting figure 4b

```{r}
figure_4b <- 
  fig_1c_nodes |> 
  mutate(type = "nodes") |> 
  bind_rows(fig_1c_edges |> 
              mutate(type = "links")) |> 
  ggplot(aes(x = year, 
             y = percentage, 
             color = type)) +
  geom_point() +
  geom_line() +
  theme(legend.position = "right", 
        text = element_text(color = "black", 
                            face = "bold",
                            family = "Times New Roman"),
        plot.title = element_text(size = 25),
        panel.background = element_rect(fill = "white"), 
        axis.text.y = element_text(size = 15, 
                                   colour = "black"),
        axis.text.x = element_text(size = 15,
                                   colour = "black", 
                                   angle = 45, vjust = 0.5
        ),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = "15"), 
        legend.title = element_blank()) +
  labs(title = "Nodes and links through time", 
       y = "Percentage") +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(2000, 2021, by = 1))

figure_4b
```

Filtering only the top 10 nodes with best degree in the first 6 clusters.

```{r}
asn_TM_connected_1 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 1) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
asn_TM_connected_2 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 2) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community))|> 
  dplyr::slice(1:10)
asn_TM_connected_3 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 3) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
asn_TM_connected_4 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 4) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
asn_TM_connected_5 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 5) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
asn_TM_connected_6 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 6) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
asn_TM_connected_7 <- 
  author_network |> 
  activate(nodes) |>
  dplyr::mutate(community = as.numeric(community)) |> 
  # filter(community >= 6) |> 
  dplyr::filter(community == 7) |> 
  # group_by(community) |> 
  dplyr::mutate(degree_community = centrality_degree()) |> 
  dplyr::arrange(desc(degree_community)) |> 
  dplyr::slice(1:10)
```

Saving the nodes we're gonna show

```{r}
nodes_community_1 <- 
  asn_TM_connected_1 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_2 <- 
  asn_TM_connected_2 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_3 <- 
  asn_TM_connected_3 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_4 <- 
  asn_TM_connected_4 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_5 <- 
  asn_TM_connected_5 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_6 <- 
  asn_TM_connected_6 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_community_7 <- 
  asn_TM_connected_7 |> 
  activate(nodes) |> 
  as_tibble() |> 
  dplyr::select(name)
nodes_selected_10 <- 
  nodes_community_1 |> 
  bind_rows(nodes_community_2, 
            nodes_community_3
            # nodes_community_4,
            # nodes_community_5,
            # nodes_community_6,
            # nodes_community_7
  )
```

Filtering selected nodes

```{r}
asn_selected_nodes <- 
  author_network |> 
  activate(nodes) |> 
  dplyr::filter(name %in% nodes_selected_10$name) 
  # dplyr::mutate(final_plot = tidygraph::group_components(type = "weak"))  
  # dplyr::filter(final_plot == 1)
```

Ploting the selected network

```{r}
figure_4c <- 
  asn_selected_nodes |> 
  activate(nodes) |> 
  dplyr::mutate(degree = centrality_degree()) |> 
  ggraph(layout = "graphopt") +
  geom_edge_link(colour = "lightgray", 
                 aes(width = weight)) +
  geom_node_point(aes(color = community, 
                      size = degree)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_graph()

figure_4c
```



